Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-11 README.Rmd
fixed a typo
updated to unzip figure

- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Update all files in the submission folder
- Finish filling in questions in ASA submission document
- Upload the files for submission and submit
- Make the repository public

@@

```{r echo = FALSE}
knitr::include_graphics("figure-readme.png")
```

@@

**Folders**

- `old-version` contains the files associated with an old version of the paper that is much longer the the submitted version.
- `submission` contains all of the files submitted to the ASA data science journal. Note that the paper is specified slightly different in this folder in order to meet the requirements of the ASA data science journal. These are as follows:
  - The figure path in the .Rnw saves the generated figures in the main folder (instead of a figures folder).

@@

- `code-file-organization.R` contains R code for organizing the files to be added to the GitHub repository and generating a file with code for submission.
- `code-paper.R` contains the R code extracted from `paper.Rnw` using code in `code-file-organization.R`.
- `code-trim-sig-data.R` contains R code for preparing the data in the file `data-example-signatures.csv.zip` based on data provided by Heike (that are not included in this directory).
- `data-bullet-test.csv.zip` and `data-bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `data-example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
- `figure-readme.png` is a figure used in the readme.
- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output. :)
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

@@

3. Knit paper (via the paper.Rnw file).
et
## Additional Information on Bullet Data

>>>>

- Remove NAs from test data
- Update readme after file changes (and practice making new submission folder, maybe create a script for copying the files)
- Finish filling in questions in ASA submission document
- Write cover letter
- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Update all files in the submission folder
- Upload the files for submission and submit
- Look into using renev

@@

```{r echo = FALSE}
unzip("figure-static/figure-readme.png.zip")
knitr::include_graphics("figure-static/figure-readme.png")
```

@@

The contents of the folders and main directory are described below:

**`code`**

Contains the R code associated with the manuscript that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):

- `data-preparation.R` contains R code for preparing the bullet training data (based on Hamby 173 and 252), bullet testing data (based on Hamby 224 sets 1 and 11), and example matching signatures (based on data provided by Heike).
- `file-organization.R` contains R code for organizing the files to be added to the GitHub repository and preparing and moving files to the submission folder.
- `paper.R` contains the R code extracted from `paper.Rnw` using code in `file-organization.R`.

**`data`**

Contains the data used to generate the manuscript:

- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.

**`figure-static`**

Contains the static figure associated with the project:

- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
- `figure-readme.png` is a figure used in the readme.

**`old-version`**

Contains the files associated with an old version of the paper that is much longer the the submitted version

**`submission`**

Contains the files submitted to the ASA data science journal. These files are moved to this folder using code in the file `code/file-organization.R`.

@@

- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output. :)
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

@@

3. Knit paper (via the paper.Rnw file).

## Additional Information on Bullet Data
